{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-14 thesis/intro.tex
revise some out of date stuff

		At all three universities I then collected statistics on the numbers and types of bugs found,
		and surveyed students to understand the human experience,
		This section will present the study's results
		to evaluate the suitability of stateless model checking in an educational setting.
	\item {\bf Transactional Memory (Chapter \ref{chap:tm}).}
		Transactional Memory (TM) is a relatively new concurrent programming technique \cite{transactional-memory}
		which is not yet addressed by modern model checkers.
		I have extended Landslide's concurrency model to support both hardware (HTM) and software (STM) variants of TM,
		and tested several ``real-world'' TM programs and benchmarks.
		This section will discuss the theoretical techniques I used to model the new form of concurrency,
		present associated correctness proofs of my approach,
		and show the testing results.
\end{enumerate}

>>>>

		At all three universities I then collected statistics on the numbers and types of bugs found,
		and surveyed students to understand the human experience,
		This section will present the study's results
		to evaluate the suitability of stateless model checking in an educational setting.
	\item {\bf Hardware Transactional Memory (HTM) (Chapter \ref{chap:tm}).}
		HTM is a relatively new concurrent programming technique \cite{transactional-memory}
		which is not yet addressed by modern model checkers.
		I have extended Landslide's concurrency model to support
		HTM's execution semantics and several advanced features, % abort codes p much
		%both hardware (HTM) and software (STM) variants of TM,
		and tested several ``real-world'' HTM programs and benchmarks.
		This section will discuss the theoretical techniques I used to model the new form of concurrency,
		present associated correctness proofs of my approach,
		and show the verification results.
\end{enumerate}

### 2018-08-14 thesis/landslide.tex
revise some out of date stuff

Therefore, Landslide's ICB implementation combines with DPOR
when tagging new branches to explore at the end of each branch:
just as DPOR skips alternate interleavings that are memory-independent,
ICB further filters interleavings requiring more preemptions than the current bound
out of the to-explore set.
The macro {\tt ICB\_BLOCKED},
defined in {\tt schedule.h},
decides if a given thread would require a preemption beyond the current bound to switch to.
The DPOR implementation then checks, for some $I_{ij}$ it wants to mark for exploration,
whether {\tt ICB\_BLOCKED(}$T_j${\tt )} at the state after $t_i$,
and skips it if so ({\tt tag\_good\_sibling()}/{\tt tag\_all\_siblings()}).
\footnote{Since ``voluntary'' context switches (e.g. arising from {\tt yield()})
are often necessary for correct execution,
{\tt ICB\_BLOCKED} does not count such switches towards the preemption count.
Therefore, within a certain preemption bound $b$,
interleavings with more than $b$ context switches may still be tested.}

>>>>

Therefore, Landslide's ICB implementation combines with DPOR
when tagging new branches to explore at the end of each branch:
just as DPOR skips alternate interleavings that are memory-independent,
ICB further filters interleavings requiring more preemptions than the current bound
out of the to-explore set.
The macro {\tt ICB\_BLOCKED},
defined in {\tt schedule.h},
decides if a given thread would require a preemption beyond the current bound to switch to%
\footnote{Since ``voluntary'' context switches (e.g. arising from {\tt yield()})
are often necessary for correct execution,
{\tt ICB\_BLOCKED} does not count such switches towards the preemption count.
Therefore, within a certain preemption bound $b$,
interleavings with more than $b$ context switches may still be tested.
}.
The DPOR implementation then checks, for some $I_{ij}$ it wants to mark for exploration,
whether {\tt ICB\_BLOCKED(}$T_j${\tt )} at the state after $t_i$,
and skips it if so ({\tt tag\_good\_sibling()}/{\tt tag\_all\_siblings()}).
